### 2018-09-12 chapter-latex/our-approach-to-the-problem.tex
added the springer chapter latex --post-review --post-response-to-review --pre-send-to-editor

>>>>

In a second pilot experiment \citep{green2013utility}, we again presented two dot arrays with the instruction in the form \emph{Choose the square with \ldots dots}. The arrays contained larger numbers of dots than in the first pilot: one array always contained 25 dots, and the other contained either 5, 10, 15, 20, 30, 35, 40, or 45 dots. Each stimulus can therefore be seen in terms of the numerical difference between the number of dots in one array and the number of dots in the other: giving numerical distances of 5, 10, 15, and 20, with smaller numerical distances resulting in less discriminable arrays and larger distances resulting in more discriminable arrays. Our main manipulation was of the vagueness of the instruction, with two levels, \emph{crisp} and \emph{vague}. Assuming the dot array [5, 25], and the instruction referring to the smaller cardinality, the \emph{crisp} instruction was \emph{Choose the square with 5 dots} and its \emph{vague} counterpart was \emph{Choose the square with few dots}. We found, as expected, that responses were faster and more accurate for vague instructions than for crisp instructions. We also found an interaction between vagueness and numerical distance such that there were diminishing returns for vagueness as numerical distance increased, until, at the biggest numerical distance, there was no real difference any more between crisp and vague instructions. We interpreted this pattern as showing that cognitive load is relatively easy in both conditions when the stimuli are most discriminable, and so vagueness confers no additional advantage in those most easily discriminable stimuli.

However, the picture painted by these findings from the second pilot experiment might be misleading. First of all, there is a possibly confounding factor. Contrast an expression from the vague condition: `the square with few dots' with an expression from the crisp condition: `the square with 5 dots'. One difference is that `few' has the potential for vagueness, whereas `5' is crisp. But another difference is that `few' is verbal while `5' is numerical, in the sense that a number is mentioned explicitly. Since these two differences could not be separated in that experiment, the finding of a vagueness advantage is vulnerable to an alternative interpretation, that the crisp-vague difference was really an advantage for the verbal form of the quantifier. In our next experiment (reported below as Experiment 1) we therefore created verbal and numeric versions of each of the vague and crisp instructions so that we could compare the crisp-vague difference and the numeric-verbal difference in the same experiment.

In Experiment 1, reported below, we also addressed another issue with the second pilot experiment: participants chose one of two dot arrays - therefore the `vague' quantifiers (few and many) uniquely identified one square. Recall our definition of vague  -- ``a word is precise if it describes a well-defined set of objects. By contrast, a word is vague if it is not precise''. The quantifiers few and many might not have realised their potential for vagueness in the context of a choice between (only) two alternatives - where there is no borderline alternative that could result in few and many being "not well-defined". Furthermore using definite articles in the instructions may have reinforced the participant's impression that only one choice counted as correct, and this impression could have been reinforced by the use of error feedback.

In the experiments we report below (Experiments 1, 2 and 3) we used what we learned from the pilot experiments to design situations that we believe did address the difference between crisp and vague instructions while taking account of the most important alternative explanations of this crisp-vague difference.
